Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-02-24 doc/manuscript/ESSDmanuscript.Rmd
temporary solution for Appendix tables
moved big tables to the end so that they're out of the way, but not yet following the template/ does not get the numbering right

bibliography: references.bib
running:
  title: IPCC forest C accounting with ForC
  author: Williams et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company. 
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #  use this to add a statement when having only software code available
  #  use this to add a statement when having only data sets available
  #code: |
  #data: |
  codedata: |
    use this to add a statement when having data sets and software code available
authorcontribution: |
  (fill this in)
disclaimer: |
acknowledgements: |
  Thank you to all researchers who collected and published the data contained in ForC, and to all research assistants and collaborators who have helped to build the database.
  Funding for this study was provided by Bezos Earth Fund to The Nature Conservancy, the Institute for Global Environmental Strategies, WLS(?)
appendix: |
output:
  rticles::copernicus_article: default
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
---

@@

\clearpage
```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)

@@

\conclusions[Conclusions]

@@

>>>>

bibliography: references.bib
running:
  title: IPCC forest C accounting with ForC
  author: Williams et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company. 
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #  use this to add a statement when having only software code available
  #  use this to add a statement when having only data sets available
  #code: |
  #data: |
  codedata: |
    use this to add a statement when having data sets and software code available
authorcontribution: |
  (fill this in)
disclaimer: |
acknowledgements: |
  Thank you to all researchers who collected and published the data contained in ForC, and to all research assistants and collaborators who have helped to build the database.
  Funding for this study was provided by Bezos Earth Fund to The Nature Conservancy, the Institute for Global Environmental Strategies, WLS(?)
appendix: |
   \section{Mapping ForC to EFDB}

   CURRENT TABLE 2 GOES HERE

   \section{Updates to ForC}

   CURRENT TABLE 3 GOES HERE

output:
  rticles::copernicus_article: default
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
---

@@

@@

# Conclusions

@@

\clearpage
# Appendix A 
<!--remove number-->

```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)

\clearpage
# Appendix B
<!--remove number-->
